Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-09-18 prob.tex
prob.tex Updating here and there...

The Bondareva-Shapley theorem can be used to algorithmically decide
non-empty core because the minimal balanced sets can be generated
by an algorithm~\cite{Peleg1965}. However, the number of minimal
balanced sets grows very rapidly with $\left|\Omega\right|$, the
size of $\Omega$~\cite{Shapley1967,Zhao2008}\footnote{\yutsung{Prove the number of minimal balanced sets grow exponentially?}},
so that we have only verified every interval-valued probability measure
has a non-empty core when $\left|\Omega\right|\le5$ so far.

@@

Mathematically, to fix the magnetic field of the Stern-Gerlach experiment
is to pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
for a given Hilbert space~$\Hilb$ of dimension~$d$. If the state
of the silver atom is represented by a density matrix~$\rho$ written
in the same basis, i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
As we discussed in the last paragraph, the Born rule of the mixed
state~$\rho$induces a classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
on $\Omega$. Let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
be the quantum event corresponding to subspace span by $E$, we can
have
\begin{equation}
\pmeas'\left(E\right)=\mu_{\rho}^{B}\left(P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}\textrm{ .}\label{BornRule.mixed-1}
\end{equation}
By equation (\ref{eq:Radon-Nikodym}), the Radon-Nikodym derivative
of $\pmeas'$ $f:\Omega\rightarrow[0,1]$ is just the diagonal elements
of $\rho$:

\begin{equation}
f\left(\ket{\psi_{j}}\right)=r_{jj}\textrm{ .}\label{eq:quantum-Radon-Nikodym}
\end{equation}

In this sense, the Radon-Nikodym derivative~$f$ is a special case
of the density matrix~$\rho$, and the Radon-Nikodym theorem is a
special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.

>>>>

The Bondareva-Shapley theorem can be used to algorithmically decide
non-empty core because the minimal balanced sets can be generated
by an algorithm~\cite{Peleg1965}. However, the number of minimal
balanced sets grows very rapidly with $\left|\Omega\right|$, the
size of $\Omega$~\cite{Shapley1967,Zhao2008}\footnote{\yutsung{Prove the number of minimal balanced sets grow exponentially
or more?}}, so that we have only verified every interval-valued probability
measure has a non-empty core when $\left|\Omega\right|\le5$ so far.\footnote{\yutsung{The program for $\left|\Omega\right|=6$ is running now.
It seems that it will not blow up the memory, but I still have no
idea when it will finish, and whether the result will be in our side
or not...?}}

@@

Mathematically, to fix the magnetic field of the Stern-Gerlach experiment
is to pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
for a given Hilbert space~$\Hilb$ of dimension~$d$, and the state
of the silver atom can be represented by a density matrix~$\rho$
written in the same basis, i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
As we discussed in the last paragraph, the Born rule of the mixed
state~$\rho$ induces a classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
on $\Omega$. Let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
be the quantum event corresponding to subspace span by $E$, we can
have
\begin{equation}
\pmeas'\left(E\right)=\mu_{\rho}^{B}\left(P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}\textrm{ .}\label{BornRule.mixed-1}
\end{equation}
By equation (\ref{eq:Radon-Nikodym}), the Radon-Nikodym derivative
of $\pmeas'$ is $f\left(\ket{\psi_{j}}\right)=r_{jj}$, which is
just the diagonal elements of $\rho$. In this sense, the Radon-Nikodym
derivative~$f$ is a special case of the density matrix~$\rho$,
and the Radon-Nikodym theorem is a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.
